Who does big team science?

### 2023-08-29 manuscript_scopus.Rmd
update the pictures for reading

keywords          : "big team, science, authorship, credit"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
bibliography: references.bib
# header-includes:
# csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
# documentclass     : "apa7"
output            : papaja::apa6_docx
appendix          :
  - "appendix.Rmd"
---

@@

```

```{r data, include = FALSE}
# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
              "snip", "ASJC_codes", "snip_all")

@@

According to the Oxford English dictionary, collaboration is two or more
people working together to achieve a certain goal [@oed2016].
Collaboration in scientific endeavors involves multiple researchers at
(potentially) multiple institutions to communicate and work together to
advance knowledge in their chosen field. Collaboration can manifest
uniquely in each project dependent on the skill sets, hypotheses, and
perspectives of collaborators. While collaboration is not new in
science, the current interest of "big team science" is increasing
[@forscher2020; @stewart2017; @coles2022]. Big team science projects
and/or organizations utilize and run on large-scale collaboration to
ensure that diverse populations and ideas are brought into research
projects, which in turn allows for more reliability and generalizability
in the results and method of the study.

BTS appears to be expanding as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) expanding interest in reproducibility, replication,
and generalizability [@maxwell2015; @nelson2018; @zwaan2018].
Technological advances have provided easier ways to collaborate with
people who are from other universities and countries through document
sharing platforms (e.g., Google, GitHub, and the Open Science
Framework), video chatting platforms (e.g., Zoom, Microsoft Teams), and
messaging and project management platforms (e.g., Slack, Trello,
when2meet, etc.). The credibility movement seems to suggest that by having both collaborations that span across the globe and subfields of research areas, age groups, and education levels should help to drive science in the path of better materials, reliability, generalizability and more robust sample sizes (when necessary) in a study [@auspurg2021has; @nosek2014method; @lebel2018].

The credibility movement was originally defined by a focus on large scale replications used in collaborative environments [@vazire2022]. Generally, the movement appears to have been driven by early career
researchers (i.e., those who are within five years of their first
appointment) [@maizey2019]; however, there are no large meta-scientific
investigations on this specific topic to date. Potentially, the lack of
investigation is tied to the newness of the large-scale research in many
fields, as it is only in recent years that publications like the Open
Science Collaboration [@opensciencecollaboration2015], Many Labs
Collaborations [@klein2018; @ebersole2020; @ebersole2016;
@klein2022; @mathur2020; @buttrick2020; @skorb2020] or the first papers
from the Psychological Science Accelerator [@moshontz2018; @jones2021;
@dorison2022; @wang2021; @legate2022; @bago2022]. Generally, the researcher incentive for replication was low for three reasons. First, journals often prioritize “novel” or new results which led to rejection of replication manuscripts and publication bias [@hubbard1997; @franco2014; @nosek2012]. Second, the
"failure" to replicate was often placed on the replication team as "bad
science" rather than a careful consideration of publication biases and
(potential) questionable research practices [@ioannidis2015;
@maxwell2015; @klein2022]. Last, why should someone want to spend time and
resources on an answer we already "know" [@isager2021; @isager2021a]?

@@

The credibility movement has been mirrored by the calls for
diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
Rich, and Democratic) scientific research [@henrich2010; @newson2021;
@rad2018] by improving representation in research samples. Like the
large-scale studies in Physics [@aphilos2021; @castelnovo2018] and
Biology [@collins2003], the Social Sciences struggle to represent the
breadth of humanity across both researcher and population
characteristics. Now, grassroots organizations, such as the
Psychological Science Accelerator [@moshontz2018], ManyBabies
(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
issues by recruiting research labs from all over the globe to provide
diversity in geographic, linguistic, and researcher representation.
Publications have examined the global understanding of morality, face
processing, COVID-19 information signaling, and more [@dorison2022;
@wang2021; @legate2022; @bago2022; @jones2021; @vanbavel2022]. While
these organizations and one-time groups for BTS studies have provided an
incredible wealth of data for the scientific community, we do not yet
know exactly *who* is involved with, and benefits from, the BTS and
credibility movement. Publications on BTS generally explore challenges,
lessons learned, and the need for BTS [@forscher2020; @coles2022].

@@

*Number of journals*. The number of distinct journals big team science
articles were published in was `r journals` with `r health_journal`
journals in Health Sciences, `r physical_journal` journals in Physical
Sciences, `r social_journal` journals in Social Sciences, and
`r life_journal` journals in Life Sciences. The descriptive statistics
for the Source Normalized Impact per Paper is presented the supplemental
materials with a comparison for all papers.

@@

Publication interest area was summarized by the four large subject areas
creating a word cloud plot of the total number of publications within
the ASJCs. Figure \@ref(fig:fig-clouds) displays that the Health
Sciences tends to publish within medicine and oncology, with a
corresponding focus of cancer research and genetics for the Life
Sciences. The Physical Sciences is mostly dominated by physics research,
chemistry, and ecology. The BTS publications in the Social Sciences are
mostly within psychology, education, and health.

@@

```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area", fig.width=10, fig.height=6}

@@

median_authors <- 
  ggplot(avg_author_time, aes(Year, Med_Num_Authors, color = SubjectArea)) + 
  theme_classic() + 
  geom_point() + 
    ylab("Median Number of Authors") + 
    xlab("Publication Year")

mean_authors <- 
  ggplot(avg_author_time, aes(Year, Average_Num_Authors, color = SubjectArea)) + 
  theme_classic() + 
  geom_point() + 
    ylab("Average Number of Authors") + 
    xlab("Publication Year")

@@

Negative career length slopes would indicate more young scholars in
later years (i.e., lower average career length as time increases).
Positive career length slopes would indicate older scholars in later
years (i.e., higher average career length as time increases). Negative
career variance slopes imply that variability decreases over the years,
so the average career length is more homogeneous. Positive career length
slopes imply that variability increases over the years, so the average
career length is varied across individuals (i.e., different stages of
scholars). Figure \@ref(fig:fig-heatmap) displays the results for all
regression analyses to compare coefficient strength across and within
hypothesis.

All values for this analyses were different from zero. The slopes for
the average career length were negative for all four subject areas,
indicating a trend toward younger scientist involvement over time for
each area, with the strongest effect in the Physical Sciences. The
coefficient for variability in career length was also negative for each
of the four subject areas with the highest in the Physical Sciences and
lowest in the Life Sciences. This result indicates a decrease in the
variability of career lengths over time, likely from two sources: 1)
more publications with more authors, thus, lowering variance
estimations, and 2) more young scholars overall. The effect sizes for
this analysis were surprisingly large ranging from $R^2$ to .25 to .47.
All values and their confidence intervals can be found on our OSF page.

```{r fig-career, include = TRUE, fig.cap = "Average career length for big-team science authors. Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year. The data has been filtered to at least 10 publications in a year for this graph.", fig.width=10, fig.height=6}
ggplot(DF$career_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         filter(num_papers >= 10) %>% 
         filter(Year < 2024), 
       aes(Year, avg_career, color = SubjectArea)) +
  theme_classic() + 
  geom_point(aes(size = sd_career)) +
  # geom_point() + 
  # facet_wrap(~SubjectArea) + 
  theme(legend.position = "bottom") + 
  ylab("Average Career Length") +
  xlab("Year of Publication") + 
  scale_color_brewer(palette = "Spectral", name = "Subject Area") +
  guides(size = "none")  
  #scale_size_continuous(name = "Number Papers")

@@

```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity in region. The top figure represents all results together for comparison across analyses. The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions. Non-significant results are indicated with NS on the plot.", fig.width=10, fig.height=6}
graph_overall <- graph_data %>% 
  bind_rows(graph_data_2) %>% 
  bind_rows(graph_data_3) %>% 
  mutate(type = factor(type, levels = c("Effect Size", "SD Coefficient", "Coefficient"))) %>% 
  mutate(Estimate = estimate) %>% 
  mutate(heat_label = ifelse(
    low < .00001 & high > .00001, "NS", ""
  ))

heat_results <- ggplot(graph_overall, aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b$"))) + 
  ylab("") + 
  xlab("") + 
  facet_wrap(~analysis) + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right", 
        legend.key.size = unit(.75, 'cm')) + 
  scale_fill_distiller(palette = "Spectral") + 
  geom_text(aes(label=heat_label))

@@

heat_results_1 <- ggplot(graph_overall %>% 
                           filter(analysis == "Career"), 
                         aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
  ylab("") + 
  xlab("") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right") + 
  scale_fill_distiller(palette = "RdBu") + 
  ggtitle("Career")  + 
  geom_text(aes(label=heat_label))

heat_results_2 <- ggplot(graph_overall %>% 
                           filter(analysis == "Publication"), 
                         aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
  ylab("") + 
  xlab("") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right") + 
  scale_fill_distiller(palette = "PuOr") + 
  ggtitle("Publication") + 
  geom_text(aes(label=heat_label))

heat_results_3 <- ggplot(graph_overall %>% 
                           filter(analysis == "Regions"), 
                         aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b$"))) + 
  ylab("") + 
  xlab("") + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right") + 
  scale_fill_distiller(palette = "PiYG") +
  ggtitle("Regions") + 
  geom_text(aes(label=heat_label))

layout <- "
AAA
BCD
"
suppressWarnings(heat_results + 
  heat_results_1 + heat_results_2 + heat_results_3 + 
  plot_layout(design = layout))

@@

The average number of publications by authors on big team sciences
papers is *M* = `r avg_pub_count_author` (*SD* =
`r std_pub_count_author`). The publication counts were averaged across
authors for each publication, and then these average publication counts
were averaged across publications *M* = `r avg_pub_count_paper` (*SD* =
`r sd_pub_count_paper`). The average variability (i.e., the average
standard deviation with authors of a manuscript) with publication counts
of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
`r SD_SD_pub_count_paper`).

@@

# map of binned data 
bin_country <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  # scale_fill_manual(name = "Sample Size",
  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral", drop = FALSE)

@@

# map of binned data 
bin_country_all <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned_all), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  # scale_fill_manual(name = "Sample Size",
  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral", drop = FALSE)

@@

```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications.", fig.width=10, fig.height=6}
bin_country + ggtitle("Big-Team Publication Map") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = "none") + 
tree + ggtitle("Big-Team Publication Mosiac Chart") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill = "none") + 
bin_country_all + ggtitle("All Publications Map") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill = "none") + 
tree_all + ggtitle("All Publications Mosiac Chart") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill = "none") + 
  plot_layout(ncol = 2, 
              nrow = 2) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

@@

Author geopolitical region is displayed in Figure
\@ref(fig:fig-map-both). Big team publications appear to be lead by
North America and Western Europe, while all publications are lead by
North America and East Asia. To understand the change in representation
diversity, we examined if the number of regions in a publication is
predicted by the year of publication. Increasing diversity would be
represented by a positive slope, while decreasing diversity would be
represented by a negative slope. As shown in Figure
\@ref(fig:fig-heatmap), the Physical Sciences do not show a trend of
change in representation, while all other sciences showed a positive
effect increasing in the number of geopolitical regions authors
represent on publications.

@@

small_dot <- ggplot(small_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

small_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() + 
  facet_grid(~Decade) + 
  xlab("Author Type") + 
  ylab("Percent of Authors") + 
  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
```

@@

medium_dot <- ggplot(medium_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

medium_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() + 
  facet_grid(~Decade) + 
  xlab("Author Type") + 
  ylab("Percent of Authors") + 
  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
```

@@

large_dot <- ggplot(large_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

large_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() + 
  facet_grid(~Decade) + 
  xlab("Author Type") + 
  ylab("Percent of Authors") + 
  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
```

```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical region across decades. F stands for first authors and O stands for other authors.", fig.width=10, fig.height=6}
small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

>>>>

keywords          : "big team, science, authorship, credit"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
bibliography: references.bib
# header-includes:
csl               : "includes/nature.csl"
# documentclass     : "apa7"
output            : papaja::apa6_pdf
appendix          :
  - "appendix.Rmd"
---

@@

# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
              "snip", "ASJC_codes", "snip_all")

@@

According to the Oxford English dictionary, collaboration is two or more
people working together to achieve a certain goal [@oed2016].
Collaboration in scientific endeavors involves multiple researchers at
(potentially) multiple institutions to communicate and work together to
advance knowledge in their chosen field. Collaboration can manifest
uniquely in each project dependent on the skill sets, hypotheses, and
perspectives of collaborators. While collaboration is not new in
science, the current interest of "big team science" is increasing
[@coles2022; @forscher2022a; @stewart2017]. Big team science projects
and/or organizations utilize and run on large-scale collaboration to
ensure that diverse populations and ideas are brought into research
projects, which in turn allows for more reliability and generalizability
in the results and method of the study.

BTS appears to be expanding as a result of two sources: 1) increasing
globalization and technology that allows for real-time interdisciplinary
research, and 2) expanding interest in reproducibility, replication, and
generalizability [@maxwell2015; @nelson2018; @zwaan2018]. Technological
advances have provided easier ways to collaborate with people who are
from other universities and countries through document sharing platforms
(e.g., Google, GitHub, and the Open Science Framework), video chatting
platforms (e.g., Zoom, Microsoft Teams), and messaging and project
management platforms (e.g., Slack, Trello, when2meet, etc.). The
credibility movement seems to suggest that by having both collaborations
that span across the globe and subfields of research areas, age groups,
and education levels should help to drive science in the path of better
materials, reliability, generalizability and more robust sample sizes
(when necessary) in a study [@auspurg2021]; @nosek2014method;
@lebel2018].

The credibility movement was originally defined by a focus on large
scale replications used in collaborative environments [@vazire2022].
Generally, the movement appears to have been driven by early career
researchers (i.e., those who are within five years of their first
appointment) [@maizey2019]; however, there are no large meta-scientific
investigations on this specific topic to date. Potentially, the lack of
investigation is tied to the newness of the large-scale research in many
fields, as it is only in recent years that publications like the Open
Science Collaboration [@opensciencecollaboration2015], Many Labs
Collaborations [@buttrick2020; @ebersole2016; @ebersole2020; @klein2018;
@klein2022; @mathur2020; @skorb2020] or the first papers from the
Psychological Science Accelerator [@bago2022; @buchanan2023;
@dorison2022; @jones2021;
@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
@moshontz2018; @wang2021]. Generally, the researcher incentive for
replication was low for three reasons. First, journals often prioritize
"novel" or new results which led to rejection of replication manuscripts
and publication bias [@franco2014; @hubbard1997; @nosek2012]. Second,
the "failure" to replicate was often placed on the replication team as
"bad science" rather than a careful consideration of publication biases
and (potential) questionable research practices [@klein2022;
@maxwell2015]. Last, why should someone want to spend time and resources
on an answer we already "know" [@isager2021; @isager2021a]?

@@

The credibility movement has been mirrored by the calls for
diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
Rich, and Democratic) scientific research [@henrich2010; @newson2021;
@rad2018] by improving representation in research samples. Like the
large-scale studies in Physics [@aphilos2021; @castelnovo2018] and
Biology [@collins2003], the Social Sciences struggle to represent the
breadth of humanity across both researcher and population
characteristics. Now, grassroots organizations, such as the
Psychological Science Accelerator [@moshontz2018], ManyBabies
(<https://manybabies.github.io/>), NutNet (<https://nutnet.org/>), and
DRAGNet (<https://dragnetglobal.weebly.com/>) can begin to tackle these
issues by recruiting research labs from all over the globe to provide
diversity in geographic, linguistic, and researcher representation.
Publications have examined the global understanding of morality, face
processing, COVID-19 information signaling, and more [@bago2022;
@dorison2022; @jones2021;
@psychologicalscienceacceleratorself-determinationtheorycollaboration2022;
@vanbavel2022; @wang2021]. While these organizations and one-time groups
for BTS studies have provided an incredible wealth of data for the
scientific community, we do not yet know exactly *who* is involved with,
and benefits from, the BTS and credibility movement. Publications on BTS
generally explore challenges, lessons learned, and the need for BTS
[@forscher2022a; @coles2022].

@@

*Number of journals*. The number of distinct journals big team science
articles were published in was `r journals` with `r health_journal`
journals in Health Sciences, `r physical_journal` journals in Physical
Sciences, `r social_journal` journals in Social Sciences, and
`r life_journal` journals in Life Sciences. The descriptive statistics
for the Source Normalized Impact per Paper is presented in the
supplemental materials with a comparison for all papers.

@@

Publication interest area was summarized by the four large subject areas
creating a word cloud plot of the total number of publications within
the ASJCs. Figure \@ref(fig:fig-clouds) displays that the Health
Sciences tends to publish within medicine and oncology, with a
corresponding focus of cancer research and genetics for the Life
Sciences. The Physical Sciences was mostly dominated by physics
research, chemistry, and ecology. The BTS publications in the Social
Sciences are mostly within psychology, education, and health.

@@

```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area. Larger words indicate more publications in those ASJC areas. ", fig.width=10, fig.height=6}

@@

median_authors <- 
  ggplot(avg_author_time, aes(Year, Med_Num_Authors, color = SubjectArea)) + 
  theme_classic(base_size = 15) + 
  geom_point() + 
    ylab("Median Number of Authors") + 
    xlab("Publication Year")

mean_authors <- 
  ggplot(avg_author_time, aes(Year, Average_Num_Authors, color = SubjectArea)) + 
  theme_classic(base_size = 15) + 
  geom_point() + 
    ylab("Average Number of Authors") + 
    xlab("Publication Year")

@@

Negative career length slopes would indicate more young scholars in
later years (i.e., lower average career length as time increases).
Positive career length slopes would indicate older scholars in later
years (i.e., higher average career length as time increases). Negative
career variance slopes imply that variability decreases over the years,
so the average career length is more homogeneous. Positive career length
slopes imply that variability increases over the years, so the average
career length is varied across individuals (i.e., different stages of
scholars). Figure \@ref(fig:fig-heatmap) displays the results for all
regression analyses to compare coefficient strength across and within
each hypothesis.

All values for these analyses were different from zero. The slopes for
the average career length were negative for all four subject areas,
indicating a trend toward younger scientist involvement over time for
each area, with the strongest effect in the Physical Sciences. The
coefficient for variability in career length was also negative for each
of the four subject areas with the highest in the Physical Sciences and
lowest in the Life Sciences. This result indicates a decrease in the
variability of career lengths over time, likely from two sources: 1)
more publications with more authors, thus, lowering variance
estimations, and 2) more young scholars overall. The effect sizes for
this analysis were surprisingly large ranging from $R^2$ = .25 to .47.
All values and their confidence intervals can be found on our OSF page.

```{r fig-career, include = TRUE,  warning = FALSE, message = FALSE, fig.cap = "Average career length for big-team science authors. Larger dots indicate more variability in career length for authors by averaging the standard deviation in career length for each manuscript within a year. The data has been filtered to at least 10 publications in a year for this graph.", fig.width=10, fig.height=6}
temp <- ggplot(DF$career_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         filter(num_papers >= 10) %>% 
         filter(Year < 2024), 
       aes(Year, avg_career, color = SubjectArea)) +
  theme_classic(base_size = 15) + 
  geom_point(aes(size = sd_career)) +
  # geom_point() + 
  # facet_wrap(~SubjectArea) + 
  theme(legend.position = "bottom") + 
  ylab("Average Career Length") +
  xlab("Year of Publication") + 
  scale_color_brewer(palette = "Spectral", name = "Subject Area") +
  guides(size = "none")  
  #scale_size_continuous(name = "Number Papers")

suppressWarnings(suppressMessages(temp))

@@

```{r fig-heatmap, include = TRUE, fig.cap="Heatmap results of regression analyses for career length, number of publications, and geopolitical diversity within the region. The top figure represents all results together for comparison across analyses. The bottom row represents individual heatmaps for each hypothesis to distinguish small differences between subject areas for those research questions. Non-significant results are indicated with NS on the plot.", warning = FALSE, message = FALSE, fig.width=10, fig.height=6}
graph_overall <- graph_data %>% 
  bind_rows(graph_data_2) %>% 
  bind_rows(graph_data_3) %>% 
  mutate(type = factor(type, levels = c("Effect Size", "SD Coefficient", "Coefficient"))) %>% 
  mutate(Estimate = estimate) %>% 
  mutate(heat_label = ifelse(
    low < .00001 & high > .00001, "NS", ""
  ))

heat_results <- ggplot(graph_overall, aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b$"))) + 
  ylab("") + 
  xlab("") + 
  facet_wrap(~analysis) + 
  theme_classic(base_size = 15) + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right", 
        legend.key.size = unit(.75, 'cm')) + 
  scale_fill_distiller(palette = "Spectral") + 
  geom_text(aes(label=heat_label))

@@

heat_results_1 <- ggplot(graph_overall %>% 
                           filter(analysis == "Career"), 
                         aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
  ylab("") + 
  xlab("") + 
  theme_classic(base_size = 15) + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right") + 
  scale_fill_distiller(palette = "RdBu") + 
  ggtitle("Career")  + 
  geom_text(aes(label=heat_label))

heat_results_2 <- ggplot(graph_overall %>% 
                           filter(analysis == "Publication"), 
                         aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b_{SD}$"), TeX("$b_M$"))) + 
  ylab("") + 
  xlab("") + 
  theme_classic(base_size = 15) + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right") + 
  scale_fill_distiller(palette = "PuOr") + 
  ggtitle("Publication") + 
  geom_text(aes(label=heat_label))

heat_results_3 <- ggplot(graph_overall %>% 
                           filter(analysis == "Regions"), 
                         aes(label, type, fill = Estimate)) + 
  geom_tile(color = "white", lwd = 1.5, linetype = 1) +
  coord_fixed() + 
  scale_y_discrete(labels  = c(TeX("$R^2$"), TeX("$b$"))) + 
  ylab("") + 
  xlab("") + 
  theme_classic(base_size = 15) + 
  theme(axis.text.x = element_text(angle = 60, vjust = .5), 
        legend.position = "right") + 
  scale_fill_distiller(palette = "PiYG") +
  ggtitle("Regions") + 
  geom_text(aes(label=heat_label))

layout <- "
AAA
BCD
"
suppressMessages(suppressWarnings(heat_results + 
  heat_results_1 + heat_results_2 + heat_results_3 + 
  plot_layout(design = layout)))

@@

The average number of publications by authors on big team science papers
is *M* = `r avg_pub_count_author` (*SD* = `r std_pub_count_author`). The
publication counts were averaged across authors for each publication,
and then these average publication counts were averaged across
publications *M* = `r avg_pub_count_paper` (*SD* =
`r sd_pub_count_paper`). The average variability (i.e., the average
standard deviation with authors of a manuscript) with publication counts
of a paper was $M_{SD}$ = `r avg_SD_pub_count_paper` ($SD_{SD}$ =
`r SD_SD_pub_count_paper`).

@@

# map of binned data 
bin_country <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void(base_size = 15) + 
  # scale_fill_manual(name = "Sample Size",
  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral", drop = FALSE)

@@

# map of binned data 
bin_country_all <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned_all), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void(base_size = 15) + 
  # scale_fill_manual(name = "Sample Size",
  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral", drop = FALSE)

@@

```{r fig-map-both, include = TRUE, fig.cap="Geopolitical regions represented in big-team science publications versus all publications. The mosaic plot is grouped by UN subregion with the largest number of publications on the left and smallest on the top right. ", fig.width=10, fig.height=6}
bin_country + ggtitle("Big-Team Publication Map") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = "none") + 
tree + ggtitle("Big-Team Publication Mosiac Chart") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill = "none") + 
bin_country_all + ggtitle("All Publications Map") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill = "none") + 
tree_all + ggtitle("All Publications Mosiac Chart") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill = "none") + 
  plot_layout(ncol = 2, 
              nrow = 2) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

@@

Author geopolitical region is displayed in Figure
\@ref(fig:fig-map-both). Big team publications appear to be led by North
America and Western Europe, while all publications are led by North
America and East Asia. To understand the change in representation
diversity, we examined if the number of regions in a publication is
predicted by the year of publication. Increasing diversity would be
represented by a positive slope, while decreasing diversity would be
represented by a negative slope. As shown in Figure
\@ref(fig:fig-heatmap), the Physical Sciences do not show a trend of
change in representation, while all other sciences showed a positive
effect increasing in the number of geopolitical regions authors
represent on publications.

@@

small_dot <- ggplot(small_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic(base_size = 15) + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

small_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic(base_size = 15) + 
  facet_grid(~Decade) + 
  xlab("Author Type") + 
  ylab("Percent of Authors") + 
  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
```

@@

medium_dot <- ggplot(medium_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic(base_size = 15) + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

medium_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic(base_size = 15) + 
  facet_grid(~Decade) + 
  xlab("Author Type") + 
  ylab("Percent of Authors") + 
  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
```

@@

large_dot <- ggplot(large_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic(base_size = 15) + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

large_author <- ggplot(DF_decade_sm, aes(who, Count, fill = Country_2)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic(base_size = 15) + 
  facet_grid(~Decade) + 
  xlab("Author Type") + 
  ylab("Percent of Authors") + 
  scale_fill_brewer(name = "Region", palette = "Spectral", drop = FALSE)
```

```{r fig-author-gpe, include = TRUE, fig.cap="A comparison of author affiliation geopolitical regions across decades. F stands for first authors and O stands for other authors.", fig.width=10, fig.height=6}
small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")
